\documentclass[11pt]{article}
\usepackage{array, xcolor, lipsum, bibentry, parallel}
\usepackage[margin=3cm]{geometry}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{paralist}
\usepackage{scrextend}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}


\title{\bfseries\Huge Christopher Hughes}
\author{}
\date{}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}


\begin{document}

	\newpage
	\setcounter{page}{1}
	\noindent

\begin{LARGE}

	\noindent\textbf{Christopher Hughes}\vspace{1pt}

\end{LARGE}


\noindent\rule{\textwidth}{1pt}\vspace{9pt}

\noindent
\begin{minipage}{0.5\textwidth}
	\begin{flushleft}
		chughes@bcgsc.ca\\
		Nationality: Canadian\\ \href{https://scholar.google.com/citations?user=jPSwBGwAAAAJ}{Google Scholar Citations}
	\end{flushleft}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
	\begin{flushright}
		2477 Carolina Street, Unit 303\\
		V5T 0G8 Vancouver, Canada\\ \href{https://www.linkedin.com/in/christopher-hughes-612460133/}{LinkedIn Profile}
	\end{flushright}
\end{minipage}\vspace{18pt}

\noindent
Personal statement:\vspace{12pt}

I am a trained biochemist with extensive experience working in the life and clinical sciences fields using a wide array of molecular and microbiology techniques, next-generation sequencing, proteomics, metabolomics, and bioinformatics technologies. I am at a transition point in my career where I am hoping to move away from a research-focused career and to obtain a new position that will allow me to apply my knowledge to tackling new problems in support of an ongoing initiative or business. I believe the position advertised at Pump House Brewery would enable me to apply my existing skill set to support the brewery team in the continued production of high-quality product. My partner was born and raised in Dieppe, NB, where her family still resides, and we hope to relocate to. Below is a brief statement of my scientific and employment background. 

I obtained my PhD at the University of Western Ontario where I studied the interactions of human embryonic and induced pluripotent stem cells with their extracellular matrix environment using a combination of proteomic and molecular biology approaches. Upon completion of my PhD, I began a prestigious Interdisciplinary EIPOD fellowship at the European Molecular Biology Laborator (EMBL) in Heidelberg, Germany where I studied the dynamics of gene expression control in yeast in steady-state and stess conditions. After my time at EMBL, I pursued an exciting opportunity as the Proteomics Platform Manager in the Genome Sciences Centre within the British Columbia Cancer Agency. My primary role this position included involvement in conception, technical development, funding acquisition, project management, data analysis, and the overall provision of high-quality service and collaborative work that caters to a diverse crowd of researchers. Within a year of my joining, I had set up and optimized the purchased instrumentation to achieve robust and reliable sample processing or data acquisition, developed a range of validated pipelines for sample and data processing, laid out extensive cost models and logging tools for recapture of funds, built collaborative relationships with other researchers and industry, published peer-reviewed literature based on the clinical applications of our work, and acquired grant funding for instrumentation maintenance and new research. After success in this manager position and in pursuit of a new challenge, I transitioned to a staff scientist position in the group of Dr. Poul Sorensen at the British Columbia Cancer Agency. In this senior role I am able to conceive, pursue funding for, and execute projects that currently relate to the study of different aspects of transcriptional and translational control of cellular phenotype in bone and childhood cancers. Aside from allowing me to apply my wet- and dry-lab skills to research projects relevant to my interests, this role has given me valuable experience relating to project and student management and grant acquisition from a supervisory viewpoint.\\

\noindent
I have attached my curriculum vitae for your consideration following this letter.
%\noindent
%Best regards,\\
%\LARGE{\textit{Christopher Hughes}}

\end{document}
