\documentclass[11pt]{article}
\usepackage{array, xcolor, lipsum, bibentry, parallel}
\usepackage[margin=3cm]{geometry}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{paralist}
\usepackage{scrextend}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}


\title{\bfseries\Huge Christopher Hughes}
\author{}
\date{}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}


\begin{document}

	\newpage
	\setcounter{page}{1}
	\noindent

\begin{LARGE}

	\noindent\textbf{Christopher Hughes}\vspace{1pt}

\end{LARGE}


\noindent\rule{\textwidth}{1pt}\vspace{9pt}

\noindent
\begin{minipage}{0.5\textwidth}
	\begin{flushleft}
		chughes@bccrc.ca\\
		Nationality: Canadian\\ \href{https://scholar.google.com/citations?user=jPSwBGwAAAAJ}{Google Scholar Citations}
	\end{flushleft}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
	\begin{flushright}
		2477 Carolina Street, Unit 303\\
		V5T 0G8 Vancouver, Canada\\ \href{https://www.linkedin.com/in/christopher-hughes-612460133/}{LinkedIn Profile}
	\end{flushright}
\end{minipage}\vspace{18pt}

%\noindent
%Personal and research statement:\vspace{12pt}

I am a trained biochemist with extensive experience working in the life and clinical sciences fields using a wide array of molecular biology, sequencing, proteomics, metabolomics, and bioinformatics technologies. I strive to acquire a position that will enable me to apply my knowledge and expertise towards facilitating impactful studies that influence our knowledge of public health and complex diseases. In addition, I am increasingly driven to understand and implement ways to better translate research and scientific knowledge to be easily communicated and understood by both my colleagues and the general public.\\ 

\noindent
I obtained my PhD at the University of Western Ontario working with Dr. Gilles Lajoie where I studied the interactions of human embryonic stem cells with their extracellular matrix environment using a combination of proteomic and molecular biology approaches. Upon completion of my PhD, I began a prestigious Interdisciplinary EIPOD fellowship at the European Molecular Biology Laboratory (EMBL) in Heidelberg, Germany where I studied the dynamics of gene expression control in steady-state and stress conditions in the labs of Drs. Jeroen Krijgsveld and Lars Steinmetz using a combination of transcriptomics and proteomics approaches. After my time at EMBL, I pursued an exciting opportunity as the Proteomics Platform Manager in the Genome Sciences Centre (GSC) within BC Cancer. The Proteomics Platform at the GSC is a core facility providing a wide range of mass spectrometry and related wet- and dry-lab services for a diverse collection of basic and clinical researchers both within the institute and across Canada. My primary role in this position included project conception, technical development, funding acquisition, project management, data analysis, and the overall provision of high-quality service to a diverse crowd of researchers. When I joined the GSC, the Proteomics Platform was largely unestablished and serviced only a few individuals who were familiar with the technology. Shortly after joining, we had set up and optimized multiple routines for reliable data acquisition, standardized pipelines for data processing, laid out extensive cost models and logging tools for recapture of funds, built collaborative relationships with other researchers and industry, published peer-reviewed literature based on the clinical applications of our work, and acquired grant funding for instrumentation and research. As a result of these efforts and outreach, the core now operates as a self-sustaining operation servicing a large user-base. After success in this manager position and in pursuit of a new challenge, I transitioned to a Staff Scientist and Mass Spectrometry Service Specialist position in the group of Dr. Poul Sorensen at the British Columbia Cancer Agency. In this senior role I am able to conceive, pursue funding for, and execute projects that currently relate to the study of different aspects of transcriptional and translational control of cellular phenotype in bone and childhood cancers. Aside from allowing me to apply my wet- and dry-lab skills to research projects relevant to my interests, this role has given me valuable experience relating to project and student management and grant acquisition from a supervisory viewpoint.\\

\noindent
I have attached my curriculum vitae for your consideration following this letter.
%\noindent
%Best regards,\\
%\LARGE{\textit{Christopher Hughes}}

\end{document}
