\documentclass[11pt]{article}
\usepackage{array, xcolor, lipsum, bibentry, parallel}
\usepackage[margin=3cm]{geometry}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{paralist}
\usepackage{scrextend}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}


\title{\bfseries\Huge Christopher Hughes}
\author{}
\date{}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}


\begin{document}

	\newpage
	\setcounter{page}{1}
	\noindent

\begin{LARGE}

	\noindent\textbf{Christopher Hughes}\vspace{1pt}

\end{LARGE}


\noindent\rule{\textwidth}{1pt}\vspace{9pt}

\noindent
\begin{minipage}{0.5\textwidth}
	\begin{flushleft}
		christopher.hughes@dal.ca\\
		Nationality: Canadian\\ \href{https://scholar.google.com/citations?user=jPSwBGwAAAAJ}{Google Scholar Citations}
	\end{flushleft}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
	\begin{flushright}
		6144 Willow Street\\
		B3K 1M2 Halifax, Canada\\ \href{https://www.linkedin.com/in/christopher-hughes-612460133/}{LinkedIn Profile}
	\end{flushright}
\end{minipage}\vspace{18pt}

%\noindent
%Personal and research statement:\vspace{12pt}

I am a trained biochemist with extensive experience working in the life sciences field using a wide array of molecular biology, next-generation sequencing, proteomic, metabolomic, and bioinformatic technologies. I am seeking a position that will enable me to apply my knowledge and expertise towards facilitating impactful studies that influence our knowledge of public health and complex diseases. In addition, I am increasingly driven to improve my knowledge translation skills in order to better communicate my research and scientific knowledge to both my colleagues and the general public.\\ 

\noindent
Over the course of my career to date, I have acquired a diverse skill set related to the study complex biological systems. In my PhD, I utilized a variety of experimental techniques and approaches, including mass spectrometry (MS)-based proteomics to study the interactions of human embryonic stem cells with their extracellular matrix environment. In my post-doctoral resarch, I again employed a suite of techniques, including a variety of RNA-sequencing methods, to study the dynamics of gene expression control in steady-state and stress conditions in a yeast model system. To build on these experiences, I later pursued an exciting opportunity as the Proteomics Platform Manager at the Genome Sciences Centre (GSC) within BC Cancer where my role encompassed project conception, technical development, funding acquisition, project management, data analysis, and the overall provision of high-quality service to a diverse array of researchers and clinicians. After success in this management position and in pursuit of a new challenge, I transitioned to a senior role at BC Cancer where I was able to conceive, pursue funding for, and execute projects that relate to the study of different aspects of bone and childhood cancers using MS and numerous complementary technologies. Aside from allowing me to apply my wet- and dry-lab skills to research projects relevant to my interests, this role has given me valuable experience relating to project and student management and grant acquisition from a supervisory viewpoint. After this, I took on a new challenge as manager of the Biological Mass Spectrometry Core at Dalhousie University. This new position broadened my exposure to a wide array of biological systems and applications of mass spectrometry, specifically in the fields of metabolomics and lipidomics.\\

\noindent
Based on my previous experience and skill set, I believe I am ideally suited for the Technical Officer position. This exciting opportunity would allow me to utilize my knowledge in a variety of wet-lab technologies, project management skills, and bioinformatic expertise to positively impact a variety of projects at NRC. These skills would enable me to maintain the existing level of excellence of the research effort while also offering new opportunities for growth in the future.\\

\noindent
I have attached my curriculum vitae for your consideration following this letter.
%\noindent
%Best regards,\\
%\LARGE{\textit{Christopher Hughes}}

\end{document}
